---
title: "Craps Simulation"
format: html
---

Run 10,000 iterations of your simulation (make sure to set a seed before you start so that the results don't change). 
Use these results to answer the questions in the remainder of this document.

# Win Probability


Create a line chart showing the cumulative probability of winning at craps with iteration # on the x-axis and cumulative probability on the y-axis.
Add a dashed horizontal red line showing the [theoretical probability of winning](https://mathworld.wolfram.com/Craps.html)

```{r}

```

# Number of Rolls in a Game

It is theoretically possible (I think?) to calculate the probability distribution of the number of rolls in craps using a recurrence relation, but it is not a fun calculation. 
Use your simulation results to draw a histogram of the number of rolls in each game (regardless of game outcome).


```{r}

```

Draw a second plot that facets the histogram by game outcome.

```{r}

```


Write 2-3 sentences describing your conclusions from the two plots. 
<!-- It may help to also view the plots on a log scale so that you can see the improbable (but possible) values more clearly -->


# Conditioning on the First Roll

For each possible value of the initial roll (`point`), calculate the win probability.
Create a stacked bar chart showing the probability of winning the game conditional on the first roll value.

```{r}

```

Can you create a summary table and add in the values that end in a win or loss on the first roll?

```{r}

```

